Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia

### 2013-11-12 article/article-draft.tex
Fixed wrong argument type in context param

 For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature. Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences. Overall, we found $\approx 29580$ wikipedia article pairs that had a similarity count greater than $50$.

>>>>

 For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature. Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure. Overall, we found $\approx 29580$ wikipedia article pairs that had a similarity count greater than $50$.
